---
title: "An Example Implementation of RiTS"
author: "Rohit Kanrar"
date: "2025-06-29"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Small Scale Implementation of Simulation Experiment in Section 3

Code from the two following files are relevant for this section:  
- `code/simulation/replicated_trial.R`
- `code/simulation/replicated_trial_evaluation.R`

## Trial Optimization
### Loading Necessary Functions, Objects and Simulated Data
```{r}
source("code/function/main_function.R")
source("code/function/misc.R")
sim_choice <- readRDS("metadata/sim_choice.RData")
sim_dat <- readRDS("metadata/sim_dat.RData")
dgps <- c("low", "high")
```

### Creating a Total of 24 Cases For Choices of Hyper-parameters and DGPs

Please refer to Web Tables 1 and 3 for more details.

```{r}
tr_starts <- sim_choice$tr_start
min_prpns <- sim_choice$min_prpns
cases <- expand.grid(dgp = dgps, min_prpn = min_prpns, tr_start = tr_starts)
print(cases)
```

Cases 5 and 6 (with min_prpn = 0.05 and tr_start = 24) are extensively discussed in the main text.

```{r}
cases <- cases[5:6, ]
n_iter <- 10 # only 10 instead of 5000 for illustration
```

### Running Trial Optimization Step for 10 Replications

Only two cases are executed. Two CPU cores are enough.

```{r}
library(parallel)
num_cores <- 2
results <- mclapply(1:nrow(cases), function(i, cases, sim_choice, sim_dat, n_iter){
  # browser()
  out_dir <- "output_git/"
  N <- sim_choice$N
  K <- sim_choice$K # cannot be changed
  d <- sim_choice$d # cannot be changed
  E <- 2 # cannot be changed
  X_true <- sim_dat$X_true; X <- sim_dat$X
  beta_true_low <- sim_dat$beta_true
  beta_true_high <- 2 * beta_true_low
  placebo_arm <- sim_dat$placebo_arm
  weight <- sim_dat$weight
  design <- sim_choice$design
  reward_sig <- sim_choice$reward_sig
  
  dgp <- cases[i, "dgp"]; min_prpn <- cases[i, "min_prpn"]
  tr_start <- cases[i, "tr_start"]
  case_str <- paste("dgp", dgp, "min_prpn", min_prpn, "tr_start", tr_start, 
                    sep = "_")
  case_str0 <- paste("dgp", dgp, "min_prpn", 0.005, "tr_start", sim_choice$ate_start, 
                    sep = "_")
  rand_file_name <- paste(out_dir, "rand_sim_", case_str0, ".RData", sep = "")
  rand_mis_file_name <- paste(out_dir, "rand_mis_sim_", case_str0, ".RData", sep = "")
  
  ts_sim <- vector(mode = "list", length = n_iter)
  rand_sim <- ts_sim; rits_sim <- ts_sim; rand_mis_sim <- ts_sim; 
  ts_mis_sim <- ts_sim; rits_mis_sim <- ts_mis_sim
  if(dgp == "low"){
    beta_true <- beta_true_low
  } else{
    beta_true <- beta_true_high
  }
  for(iter in 1:n_iter){
    # if(iter %% 100 == 0) print(iter)
    seed_ <- iter
    set.seed(seed_)
    ts_sim[[iter]] <- do_ts_batch(X = X_true, X_true = X_true, beta_true = beta_true, 
                                  weight = weight, seed = seed_, rwd_sig = reward_sig,
                                  tr_start = tr_start, tr_batch = 5, tr_lag = 10,
                                  M = 1000, v = 10, min_prpn = min_prpn, asympcs = FALSE)
    rits_sim[[iter]] <- do_rits_batch(X = X_true, X_true = X_true, beta_true = beta_true, 
                                      weight = weight, seed = seed_, rwd_sig = reward_sig,
                                      tr_start = tr_start, tr_batch = 5, tr_lag = 10,
                                      M = 1000, v = 10, min_prpn = min_prpn, asympcs = FALSE)
    ts_mis_sim[[iter]] <- do_ts_batch(X = X, X_true = X_true, beta_true = beta_true, 
                                      weight = weight, seed = seed_, rwd_sig = reward_sig,
                                      tr_start = tr_start, tr_batch = 5, tr_lag = 10,
                                      M = 1000, v = 10, min_prpn = min_prpn, asympcs = FALSE)
    rits_mis_sim[[iter]] <- do_rits_batch(X = X, X_true = X_true, beta_true = beta_true, 
                                          weight = weight, seed = seed_, rwd_sig = reward_sig,
                                          tr_start = tr_start, tr_batch = 5, tr_lag = 10,
                                          M = 1000, v = 10, min_prpn = min_prpn, asympcs = FALSE)
    if(min_prpn == 0.005){
      rand_sim[[iter]] <- do_rand_biv(X = X_true, X_true = X_true, beta_true = beta_true, 
                                      weight = weight, seed = seed_, 
                                      rwd_sig = reward_sig, tr_start = tr_start,
                                      asympcs = FALSE)
      rand_mis_sim[[iter]] <- do_rand_biv(X = X, X_true = X_true, beta_true = beta_true, 
                                          weight = weight, seed = seed_, 
                                          rwd_sig = reward_sig, tr_start = tr_start,
                                          asympcs = FALSE)
    }
  }
  saveRDS(ts_sim, paste(out_dir, "ts_sim_", case_str, ".RData", sep = ""))
  saveRDS(rits_sim, paste(out_dir, "rits_sim_", case_str, ".RData", sep = ""))
  saveRDS(ts_mis_sim, paste(out_dir, "ts_mis_sim_", case_str, ".RData", sep = ""))
  saveRDS(rits_mis_sim, paste(out_dir, "rits_mis_sim_", case_str, ".RData", sep = ""))
  if(min_prpn == 0.005){
    saveRDS(rand_sim, paste(out_dir, "rand_sim_", case_str0, ".RData", sep = ""))
    saveRDS(rand_mis_sim, paste(out_dir, "rand_mis_sim_", case_str0, ".RData", sep = ""))
  }
  return(NULL)
}, mc.cores = num_cores, cases = cases, sim_dat = sim_dat, sim_choice = sim_choice, n_iter = n_iter)
```

## Trial Evaluation
### Loading Necessary Functions, Objects and Simulated Data
```{r}
source("code/function/main_function.R")
source("code/function/misc.R")
source("code/function/classical_ci.R")
source("code/function/asymp_cs.R")

batch <- 1
```

### Adding AsympCS and T-Test CI in Output Files from Trial Optimization Step 

```{r}
library(parallel)
num_cores <- 2
results <- mclapply(1:nrow(cases), function(i, cases, sim_choice){
  # browser()
  out_dir <- "output_git/"
  dgp <- cases[i, "dgp"]; min_prpn <- cases[i, "min_prpn"]
  tr_start <- cases[i, "tr_start"]
  case_str <- paste("dgp", dgp, "min_prpn", min_prpn, "tr_start", tr_start, 
                    sep = "_")
  mods <- c("rand_sim", "ts_sim", "rits_sim", "rand_mis_sim", "ts_mis_sim", 
            "rits_mis_sim")
  for(mod in mods){
    file_name <- paste(out_dir, mod, "_", case_str, ".RData", sep = "")
    if(file.exists(file_name)){
      out_sim <- readRDS(file_name)
      out_sim <- add_asympcs_sim(out_list = out_sim, ate_start = 24, batch = batch, 
                                 placebo_arm = 1, alpha = 0.05, first_peek = 50, 
                                 n_cores = 1, force_compute = TRUE)
      out_sim <- add_standard_ci(out = out_sim, ate_start = 24, batch = batch, 
                                 placebo_arm = 1, alpha = 0.05, force_compute = TRUE)
      saveRDS(out_sim, file_name) 
    } else{
      next
    }
  }
  return(NULL)
}, mc.cores = num_cores, cases = cases, sim_choice = sim_choice)
```


## Generate All Plots

### Main Text
```{r}
source("code/visualization/main_viz.R")
```
Figure numbers and `R` objects are matched below from the above `R` script.
- Figure 1: Used PowerPoint
- Figure 2: `sim_regret_plot`
- Figure 3: `metric_alloc_plot`
- Figure 4: `metric_alloc_plot_real`

### Web Appendix
```{r}
source("code/visualization/appendix_viz.R")
```
Figure numbers and `R` objects are matched below from the above `R` script.
- Web Figure 1: `sim_wid`
- Web Figure 2: `sim_bias`
- Web Figure 3: `cum_miscov`
- Web Figure 4: `sim_regret_plot`
- Web Figure 4: `sim_regret_plot`


## Generate All Tables

### Main Text (Table 1)
```{r}
source("code/visualization/main_tab.R")
est_err_tab <- rbind(est_err_tab_high, est_err_tab_low) # Table 1
```
Only one table is included in the main text.


### Web Appendix
```{r}
source("code/visualization/appendix_tab.R")
table2 <- rbind(est_err_all_mis_tab[[6]]$tab, est_err_all_mis_tab[[5]]$tab)
```
Table numbers and `R` objects are matched below from the above chunk of `R` code.
- Web Table 1: `cum_miscov_all_tab`
- Web Table 2: `table2`
- Web Table 3: `cum_miscov_all_mis_tab`